Theory of Phonon Polaritons in Polar Dielectrics

### 2018-08-06 paper.tex
fixed ref compile issue

Phonon polaritons, hybrid quasiparticles of photons and optical phonons, offer great promise for deeply sub-diffractional control of electromagnetic fields at mid-IR and THz frequencies. These polaritons share many features in common with plasmon-polaritons in conductors, a heavily well-studied topic. In recent years, it has been shown that phonon polaritons offer the ability to confine light to volumes over $10^6$ times smaller than that of a photon in free-space at the diffraction limit \cite{caldwell2013low,xu2014mid,caldwell2014sub,dai2014tunable,tomadin2015accessing,yoxall2015direct,li2015hyperbolic,dai2015subdiffractional,dai2015graphene,caldwell2015low,li2016reversible,Basov:2016,basov2017towards,low2017polaritons,giles2017ultra}. Due to this remarkable confinement and their relatively high lifetimes of around picoseconds, phonon polaritons open new opportunities for vibrational spectroscopy, for radiative heat transfer \cite{hillenbrand2002phonon}, and for control of dynamics in quantum emitters \cite{kumar2015tunable,rivera2017making,kurman2018controlling}. Typically, the core features of phonon polaritons, such as mode shape, confinement, and propagation characteristics, can be understood through the properties of the Lorentz oscillator dielectric function, which has been successfully applied to model experiments involving the launching and propagation of these polaritons.

>>>>

Phonon polaritons, hybrid quasiparticles of photons and optical phonons, offer great promise for deeply sub-diffractional control of electromagnetic fields at mid-IR and THz frequencies. These polaritons share many features in common with plasmon-polaritons in conductors, a heavily well-studied topic. In recent years, it has been shown that phonon polaritons offer the ability to confine light to volumes over $10^6$ times smaller than that of a photon in free-space at the diffraction limit \cite{caldwell2013low,xu2014mid,caldwell2014sub,dai2014tunable,tomadin2015accessing,yoxall2015direct,li2015hyperbolic,dai2015subdiffractional,dai2015graphene,caldwell2015low,li2016reversible,Basov:2016,basov2017towards,low2017polaritons,giles2017ultra}. Due to this remarkable confinement and their relatively high lifetimes of around picoseconds, phonon polaritons open new opportunities for vibrational spectroscopy, for radiative heat transfer \cite{hillenbrand2002phonon}, and for control of dynamics in quantum emitters \cite{kumar2015tunable,rivera2017making,kurman2018control}. Typically, the core features of phonon polaritons, such as mode shape, confinement, and propagation characteristics, can be understood through the properties of the Lorentz oscillator dielectric function, which has been successfully applied to model experiments involving the launching and propagation of these polaritons.
